### 2022-09-28 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@168624837233208b10ef2af8dac807174a1c4161 🚀

The popularity of graph embedding techniques in machine learning is more
than the search for structural invariants: graphs are discrete objects,
and machine learning techniques tend to handle continuous data better.
Bringing a sparse graph into a continuous, dense vector space (Xu, 2020)
opens up a broader variety of predictive algorithms, notably of the sort
that are able to predict events as probabilities (Murphy, 2022).
Furthermore, the projection of the graph itself is a representation that
can be learned; Runghen et al. (2021), for example, used a neural
network to learn the embedding of a network in which not all
interactions were known, based on the nodes' metadata. This example has
many parallels in ecology (see fig.~\ref{fig:embedding} \textbf{C}), in
which node metadata can be represented by phylogeny, abundance, or
functional traits. Using phylogeny as a source of information assumes
(or strives to capture) the action of evolutionary processes on network
structure, which at least for food webs have been well documented
\textbf{TK REF}; similarly, the use of functional traits assumes that
interactions can be infered from the knowledge of trait-matching rules,
which is similarly well supported in the empirical literature \textbf{TK
REF}. Relating this information to an embedding rather than a list of
networks measures would allow to capture their effect on the more
fundamental aspects of network structure; conversely, the absence of a
phylogenetic or functional signal may suggest that evolutionary/trait
processes are not strong drivers of network structure, therefore opening
a new way to perform hypothesis testing.

@@

\leavevmode\hypertarget{ref-Xu2020UndGra}{}%
Xu, M. (2020). \emph{Understanding graph embedding methods and their
applications}. \url{http://arxiv.org/abs/2012.08019}

>>>>

The popularity of graph embedding techniques in machine learning is more
than the search for structural invariants: graphs are discrete objects,
and machine learning techniques tend to handle continuous data better.
Bringing a sparse graph into a continuous, dense vector space (Xu, 2021)
opens up a broader variety of predictive algorithms, notably of the sort
that are able to predict events as probabilities (Murphy, 2022).
Furthermore, the projection of the graph itself is a representation that
can be learned; Runghen et al. (2021), for example, used a neural
network to learn the embedding of a network in which not all
interactions were known, based on the nodes' metadata. This example has
many parallels in ecology (see fig.~\ref{fig:embedding} \textbf{C}), in
which node metadata can be represented by phylogeny, abundance, or
functional traits. Using phylogeny as a source of information assumes
(or strives to capture) the action of evolutionary processes on network
structure, which at least for food webs have been well documented
\textbf{TK REF}; similarly, the use of functional traits assumes that
interactions can be infered from the knowledge of trait-matching rules,
which is similarly well supported in the empirical literature \textbf{TK
REF}. Relating this information to an embedding rather than a list of
networks measures would allow to capture their effect on the more
fundamental aspects of network structure; conversely, the absence of a
phylogenetic or functional signal may suggest that evolutionary/trait
processes are not strong drivers of network structure, therefore opening
a new way to perform hypothesis testing.

@@

\leavevmode\hypertarget{ref-Xu2021UndGra}{}%
Xu, M. (2021). Understanding Graph Embedding Methods and Their
Applications. \emph{SIAM Review}, \emph{63}(4), 825--853.
\url{https://doi.org/10.1137/20M1386062}
